### 2020-08-14 Analysis/Code/Paper.Rmd
Corrected the wrong renormalization of Age and Score variables.

res <- plmJuliaToTex(reg1, reg2, reg.results[, c(1,4)],
                     reg.results.stats[, c(1,4)])
rm(reg.results, reg.results.stats)

>>>>

# plmJuliaToTex contains a lot of manual coding, because of the 
# difference in variable names between Julia and R codes. If you 
# change the Julia results, or reg1/reg2 regs, you would have to
# change plmJuliaToTex for this chunk to work properly
res <- plmJuliaToTex(reg1, reg2, reg.results[, c(1,4)],
                     reg.results.stats[, c(1,4)])
rm(reg.results, reg.results.stats)
